The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-27 paper2_JNLS/paper.tex
NM

 % Figure 2
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/fig2.pdf}
\caption{
(a)--(b) Surface displacement measured at a representative upstream and downstream location. (c)--(d) Corresponding histograms. Reproduced from \cite{bolles2019anomalous}
}
\label{fig2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 % Data from column 5 in MasterTimeSeries, Delta theta = 1.38 degrees

@@

%----------------------------------------------------------------------------%
% KdV
%----------------------------------------------------------------------------%
\subsection{The Korteweg–de Vries equation with variable depth}
Consider waves propagating unidirectionally in shallow water. Consider the surface displacement $\eta(x,t)$ and the reference frame moving with the local wave speed $\xi = x - ct$, where $c = \sqrt{g \depth}$ is the wave speed, $g$ gravity, and $\depth$ the local depth.
To first-correction in small amplitude, surface displacements are governed by the Korteweg–de Vries equation (KdV), which in dimensional form is given by
\begin{equation}
2 \eta_t + \frac{3 c}{\depth} \eta \eta_{\xi} + \frac{c \depth^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
% The coefficients and scales can be verified on Wolfram KdV page (but what about the sign?). I would like an official source as confirmation though.

@@

@@

Lets do the nondimensionalization generally, so that we can easily make modifications if needed. In general, we introduce dimensionless variables as
\begin{align}
&u = \eta / \ampscale
&&\mbox{\em dimensionless surface displacement} \\
&\tilde{x} = \xi / \lengthscale
&&\mbox{\em dimensionless position (moving frame)} \\
&\tilde{t} = t / \timescale
&&\mbox{\em dimensionless time}
\end{align}
where the characteristic scales $\ampscale, \lengthscale, \timescale$ for wave amplitude, length, and time respectively, are free for us to choose.
Then the dimensionless KdV equation is
\begin{equation}
u_t + \frac{3}{2} \left( \frac{c \timescale \ampscale}{\lengthscale \depth} \right) u u_x 
+ \frac{1}{6} \left( \frac{c \timescale \depth^2}{\lengthscale^3} \right) u_{xxx} = 0
\end{equation}

>>>>

 % Figure 2
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.85 \linewidth]{Figs/fig2.pdf}
\caption{
(a)--(b) Surface displacement measured at a representative upstream and downstream location. (c)--(d) Corresponding histograms. Reproduced from \cite{bolles2019anomalous}
}
\label{fig2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 % Data from column 5 in MasterTimeSeries, Delta theta = 1.38 degrees, which is in between runs 5 and 6.

@@

%----------------------------------------------------------------------------%
% KdV
%----------------------------------------------------------------------------%
\subsection{The Korteweg–de Vries equation with variable depth}
Consider waves propagating unidirectionally in shallow water. Consider the surface displacement $\eta(x,t)$ and the reference frame moving with the local wave speed $\xi = x - ct$, where $c = \sqrt{g \depth}$ is the wave speed, $g$ gravity, and $\depth$ the local depth.
To first-correction in small amplitude, surface displacements are governed by the Korteweg–de Vries equation (KdV), which in dimensional form is given by
\begin{equation}
\label{KdV}
2 \eta_t + \frac{3 c}{\depth} \eta \eta_{\xi} + \frac{c \depth^2}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
% The coefficients and scales can be verified on Wolfram KdV page (but what about the sign?). I would like an official source as confirmation though.

@@

Here, we recast the variable-depth KdV equation \eqref{KdV} in dimensionless variables.
Of course, the choice of how to nondimensionalize is not unique, and our choices will made for convenience with the Hamiltonian structure introduced in the next section. It may be instructive to be able to compare against other traditional nondimensionalizations and hence we first introduce a generic nondimensionalization: nondimensionalize 
\begin{align}
&u = \eta / \ampscale
&&\mbox{\em dimensionless surface displacement} \\
&\tilde{x} = \xi / \lengthscale
&&\mbox{\em dimensionless position (moving frame)} \\
&\tilde{t} = t / \timescale
&&\mbox{\em dimensionless time}
\end{align}
where the characteristic scales $\ampscale, \lengthscale, \timescale$ for wave amplitude, length, and time respectively, are free for us to choose.
Then the dimensionless KdV equation is
\begin{equation}
u_t + \frac{3}{2} \left( \frac{c \timescale \ampscale}{\lengthscale \depth} \right) u u_x 
+ \frac{1}{6} \left( \frac{c \timescale \depth^2}{\lengthscale^3} \right) u_{xxx} = 0
\end{equation}

@@
